Medical Concept Extraction

### 2012-12-16 paper/paper.tex
TKs for Tristan, and note regarding regression.
Adding the new system figure/

\subsubsection{Linear Regression}

@@

\subsection{High Dimensionality}

\subsection{Biased Data}

\subsection{Amount of Data}

@@

\begin{figure}
\begin{center}
	\includegraphics[width=1\columnwidth]{figures/system.png}
\end{center}
\caption{An overview of the system and codebase. TODO (SAL): Add the actual system diagram image.}
\label{fig:system}
\end{figure}

We built a fairly comprehensive framework for applying machine learning techniques to NLP domains. We built out a series of useful and reusable library modules and command line utilities to perform various tasks. An overview of the codebase can be seen in Figure~\ref{fig:system} and  all of the code is available online at the following url:

>>>>

\subsubsection{Linear Regression}
Clarification: liblinear is not doing linear regression, the default is L2-regularized SVM solver using L2-loss SVC in the dual.

@@

\subsection{High Dimensionality}
TK(TJN)

\subsection{Biased Data}
TK(TJN)

\subsection{Amount of Data}
TK(TJN)

@@

\begin{figure*}
\begin{center}
	\includegraphics[width=2\columnwidth]{figures/system.pdf}
\end{center}
\caption{An overview of the system and codebase. TODO (SAL): Add the actual system diagram image.}
\label{fig:system}
\end{figure*}

We built a fairly comprehensive framework for applying machine learning techniques to NLP domains. We built out a series of useful and reusable library modules and command line utilities to perform various tasks. An overview of the codebase can be seen in Figure~\ref{fig:system} and  all of the code is available online at the following URL:
